---
title: "ADEME"
output:
  github_document
bibliography: Bibli.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.align='center')
```

<details>
<summary>Packages</summary>
<p>

```{r}

want = c("googlesheets4",
         "purrr",
         "dplyr",
         "tidyr",
         "zoo",
         "ggplot2")

have = want %in% rownames(installed.packages())

# Install the packages that we miss
if ( any(!have) ) { install.packages( want[!have] ) }

# Load the packages
junk <- lapply(want, library, character.only = T)

# Remove the objects we created
rm(have, want, junk)


```
</details> 

# Introduction
<details>
<summary>Codes</summary>
<p>

```{r}
ADEME.data <- read_sheet("https://docs.google.com/spreadsheets/d/1LFHU66VoZtDFF2OI2Wr4-bmw_x1UQHhn9gp_TtnNkWE/edit?usp=sharing") %>%
  mutate_all(as.character)

names(ADEME.data)<-gsub("\\.","",names(ADEME.data))

p2 <- ADEME.data %>%
  select(Type, Scenario, Distances7:Distances9)%>% 
  filter(Type != "Type")  %>% 
  set_names(slice(.,1)) %>%
  slice(-1) %>% 
  pivot_longer(cols = "2015":"2050", names_to = "time", values_to = "Km_jr_hab")%>% 
  rename("Type"= "Year") %>% 
  mutate(time = as.numeric(time),
         Km_jr_hab = as.numeric(Km_jr_hab),
    diff = lead(time) - time,
    diff = ifelse(diff < 0 , 1, diff)) %>% 
    group_by(Type, Scenario, time) %>%
  slice(rep(1:n(),each = diff)) %>% 
  mutate(year =  1:n() +time -1) %>% 
     group_by(Type, Scenario, time) %>% 
   mutate(Km_jr_hab = ifelse(time != year, NA, Km_jr_hab)) %>% 
  filter(year <= 2050  ) %>% 
    group_by(Type, Scenario) %>% 
  mutate(test = na.approx(Km_jr_hab),
         Name = paste(Scenario, Type)) %>% 
   ggplot() +  
  geom_line(aes(x = year, y = test * 362.5 , group = Name, color = Name), size = 1)+
  ylab("") +
  xlab("") +
  labs(title = "ADEME scenarios", subtitle = "In km/inhab/year") +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold", size = 16),
        plot.subtitle = element_text(colour = "#595a5c", size = 12),
        legend.title = element_blank(),
        legend.text = element_text( size = 10),
        legend.position="top",
        axis.text=element_text(size=10),
        axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=1)) +
  ylim(0, 1250)

```
</details> 

From the ADEME's documentation (@ademeProjetenergiesressourcesademedecembre2020Pdf2020). The agency and its experts 

The *Agence de l'Environnement et de la Maitrise de l'Energie* (ADEME) is the french agency of the ecological transition. In short, they participate in the establishment of public policies in the environment, energy, and sustainable development domain. 

ADEME has launched a prospective project for the next two years. Compared to the previous project entitled *Visions de l'ADEME*, the new scenarios have greatly evolved with both an awareness of the climate emergency and new ambitions to be maintained in the long term (carbon neutrality in 2050) but also with the emergence of broader ecological issues (material, soils, etc.).

The main new features of the project are:

* The realization of several French transition scenarios (national + footprint) that all aim to reach
carbon neutrality, but in contrasting fashion, with an assessment of resources (materials, biomass,
soil in particular) and including a territorial component;
* A multi-criteria comparison (in particular technico-economic and environmental) of
scenarios, conditions of realization and their consequences;
* A retrospective, an inventory and trajectories up to at least 2050;
* Dialogue with external stakeholders on the consistency of all the scenarios envisaged
and enrichment of working hypotheses;
* A descriptive strategic foresight on a few key sectors in the French context.


# Visualization
```{r, echo = FALSE}
p2
```


# reference